\par
Our quiz platform is developed in a way that makes it easy to modify and it is very flexible. Because of this it can easily cover the needs of the client. Our platform also gives the client the choice of deploying it with different types of features and functionality. Also this platform is developed with innovation in mind, although a quiz in it self might not be much of a innovation, it is rather the way the quiz is created and build. That is what makes this platform unique.

Our quiz platform is a web application with a front-end written in HTML and Typescript, and a back-end written in the all new  PHP7. Our web applications is a Single Page Application (SPA) developed in the brand new and cutting edge framework, Angular 2\cite{Angular2:online}. Angular 2 gives developers the opportunity of reuse of code. This means that you basically write one code for web, mobile web, mobile native and desktop native. This Google supported framework works great with bootstrap which makes the applications very responsive and intuitive. 

In our application the users can take anything from a regular quiz to a formal exam, you can compete in a competition group or take a beginner quiz, if the quiz related topic is not your strongest. Our platform gives the users the choice to choose if they desire to either take a picture or sound quiz. They can also take a quiz called "Several sound quiz" that plays multiple sounds at once meaning there is multiple right answers as well. As the beginner quiz should be more suitable for beginners it has both pictures and sounds available to it easier to choose the correct answer.